---
title: "Dice and CDF"
output: html_document
date: "2022-10-12"
---

Are you in visual mode? (If not, switch modes.)

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

# Packages and Libraries

```{r}

install.packages('tidyverse')
install.packages('clean')

```

```{r}

library(tidyverse)
library(clean)

```

# Generate Data

## Simulate rolling dice.

Change numrolls to however many rolls you want to simulate.

```{r}

numrolls <- 
  10

sums <- 
  0 

for(i in 1:numrolls) {
  sums[i] = sample(1:6,1) + sample(1:6, 1)  
}

sums <- 
  sums %>% 
    sort() 

```

## Force Structure

```{r}

sums.cdf <- 
  sums %>% 
    ecdf() 

rolls <- 
  data.frame( 
    sums, 
    rank = sums.cdf(sums))

```

## Graph Histogram and Cumulative Density

```{r}

rolls %>% 
  ggplot( aes(x =sums)) + 
    geom_histogram( aes(y=..density..), binwidth=0.5) + 
    stat_ecdf() 

```

# Comparing Data

## Make a choice

Choose values for sum1 and sum2 OR roll dice and add to generate sum1 and sum2 randomly.

### Pick whimsically

sum1 = your choice

### Determine randomly

sum1 = (roll two dice and add)

### Set it to the mean

sum1 = mean(rolls\$sums)

## Code your choice

```{r}

sum1 = 6
  
sum2 = mean(rolls$sums)

portion <- 
  abs(sums.cdf(sum1) - sums.cdf(sum2) )

portion 

cat(sep="", "\n",portion*100, "% of the data, or ", portion*length(rolls$sums)," observations, live between ", sum1, " and ", sum2, ".\n")

```

### Graph Focus Area

```{r}

left <- 
  min(sum1, sum2)

right <-
  max(sum1, sum2)

focus_data <- 
  rolls %>% 
    filter(
      between(sums, left, right)
      ) 

rolls %>% 
  ggplot( aes(x=sums)) + 
    stat_ecdf() + 
    geom_vline(xintercept = sum1, col="blue") + 
    geom_vline(xintercept = sum2, col="green") + 
    geom_hline(yintercept = sums.cdf(sum1), col="blue") + 
    geom_hline(yintercept = sums.cdf(sum2), col="green")

rolls %>% 
  ggplot( aes(x=sums)) + 
    geom_histogram(binwidth = 0.5) + 
    geom_histogram(data = focus_data, fill="violet", binwidth = 0.5) +
    geom_vline(xintercept = sum1, col="blue") + 
    geom_vline(xintercept =sum2, col="green") 

```

# Summarize data with frequency function

```{r}

sums %>% 
  freq() 



```
